### 2020-05-28 sc20_reviews/response.md

  * We added the Deakin citation to our related work.

## Reviewer 4

  * Text has been added to Section II to clarify validation.

  * We clarified the quote about 50% in Section IV.

  * We clarified the paragraph at the top of Section V.A.

  * We expanded Section VI.

@@

## Reviewer 5

  * We added Section V.G.

  * Figure 11 is comparable to Figure 3. As described in the text, Figure 3 is generated from Figure 2 by computing, for each data point, efficiency and task granularity. These are derived metrics, resulting in a parametric graph. Intuitively, there is a data point per problem size, but task granularity does not necessarily decrease with problem size. This view makes it intuitive how efficiency and task granularity are related.

### 2020-05-28 sc20_reviews/response.md

## Reviewer 5

  * We added Section V.G.

  * Figure 11 is comparable to Figure 3. As described in the text, Figure 3 is generated from Figure 2 by computing, for each data point, efficiency and task granularity. These are derived metrics, resulting in a parametric graph. Intuitively, there is a data point per problem size, but task granularity does not necessarily decrease with problem size. This view makes it intuitive how efficiency and task granularity are related.

  * We use MPS in the case of MPI with 4 ranks per GPU. Our code uses an offload model where any communicated data is copied to and from the GPU for each task execution; this is an intentional decision to model the most common way in which MPI+CUDA is used. Using 4 ranks per node allows the copies to/from the GPU and kernel launches to be performed in parallel, increasing the utilization of the GPU (at the cost of higher overheads at small task granularities).

### 2020-05-28 sc20_reviews/response.md

  * We clarified the paragraph at the top of Section V.A.

  * We expanded Section VI.

## Reviewer 5

  * Whether dependencies are constructured ahead of time or on the fly is a feature of a specific implementation of Task Bench, not the core API.

    FIXME: Add note about added Dask/TensorFlow impls, or whether we add more text, or whatever.

@@

  * We added Section V.G.

  * Figure 11 is comparable to Figure 3. As described in the text, Figure 3 is generated from Figure 2 by computing, for each data point, efficiency and task granularity. These are derived metrics, resulting in a parametric graph. Intuitively, there is a data point per problem size, but task granularity does not necessarily decrease with problem size. This view makes it intuitive how efficiency and task granularity are related.

  * We use MPS in the case of MPI with 4 ranks per GPU. Our code uses an offload model where any communicated data is copied to and from the GPU for each task execution; this is an intentional decision to model the most common way in which MPI+CUDA is used. Using 4 ranks per node allows the copies to/from the GPU and kernel launches to be performed in parallel, increasing the utilization of the GPU (at the cost of higher overheads at small task granularities). All of these factors, including the kernel launch latency, are included in our task granularity measurements.

### 2020-05-29 1_introduction.tex
Update related work.
Try out some new text in the introduction.

One approach to comparing performance is through \emph{proxy-} or
\emph{mini-apps}. Because they distill key computational characteristics of larger
applications, mini-apps offer insight
without the expense of developing production codes. However, despite the name, our experience is that
mini-apps still require significant investment to develop
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop a correct implementation. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Few published studies compare more than a handful of systems~\cite{LULESH13}.

>>>>

{\color{blue}

Existing approaches to comparing performance focus on \emph{mini-apps}
or \emph{microbenchmarks}. These smaller codes distill key
computational characteristics of larger applications: mini-apps are
often derived from a larger code, and thus directly inherit its
behaviors, while benchmarks are typically chosen to reflect a more
narrow set of behaviors. In either case, while a variety of insight
can be gained, the overall effort required is proportional to the
product of the number of systems and behaviors one would like to
evaluate. As a result, few published studies compare more than a
handful of systems~\cite{LULESH13, Deakin19}.

}

\zap{
One approach to comparing performance is through \emph{proxy-} or
\emph{mini-apps}. Because they distill key computational characteristics of larger
applications, mini-apps offer insight
without the expense of developing production codes. However, despite the name, our experience is that
mini-apps still require significant investment to develop
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop a correct implementation. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Few published studies compare more than a handful of systems~\cite{LULESH13, Deakin19}.
} % zap
